---
title: "Shiny Example for BDAH 2014"
date: "Tuesday, July 22, 2014"
output: html_document
runtime: shiny
---

### Introduction
By writing a Shiny document, you provide your users with the option of exploring
the data on their own. Shiny documents allow your users to interact with your
data and immediately see the output of their changes, in the form of 

* plots, 
* tables,
* text, 
* and even in the form of models!

The input and output are typically in the form of a web-page, but there is no
need to learn Javascript or HTML!

### Exploring the FHS Data
In this document, we shall provide the user with the options of exploring the
relationship between 3 explanatory variables and 3 responses. As the responses
are binary, the plot includes a fitted logistic regression line, and also allows
for conditioning on gender. 

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
fhs.long <- read.csv("../data/frmgham2.csv")
fhs.only3 <- filter(fhs.long, PERIOD==3)
```

```{r, echo=FALSE}
inputPanel(
  radioButtons("x_var", label="Explanatory Variable", 
    choices=c("BMI", "LDLC", "TOTCHOL"), selected="BMI"),
  
  radioButtons("y_var", label="Response Variable", 
    choices=c("CVD", "STROKE", "ANYCHD"), selected="CVD"),
  
  checkboxInput("con_gender", label="Condition on Gender", value=FALSE)
)

inputPanel(
  sliderInput("bmi_range", label="BMI range", min=10,
  max=60, value=c(10,60)),
  sliderInput("ldlc_range", label="LDLC range", min=20,
  max=565, value=c(20,565)),
  sliderInput("tot_range", label="Total Chol. range", min=112,
  max=625, value=c(112,625))
)

renderPlot({
  x <- fhs.only3[,input$x_var]
  y <- fhs.only3[,input$y_var]
  
  if(input$x_var == "BMI") {
    x.range <- input$bmi_range
  } else if (input$x_var == "LDLC") {
    x.range <- input$ldlc_range
  } else 
    x.range <- input$tot_range
  
  if(input$con_gender){
    p <- qplot(x,y, xlab=input$x_var, ylab=input$y_var, facets = . ~ SEX, data=fhs.only3)
  } else {
    p <- qplot(x,y, xlab=input$x_var,ylab=input$y_var) 
  } 
  #p + geom_point(size=3, colour="steelblue")
  p + xlim(x.range) + stat_smooth(method="glm", family="binomial") + 
  geom_point(position=position_jitter(height=0.02)) 
})
```
